---
title: "TM-Visuals"
author: "Zoey"
date: '2022-04-03'
output: word_document
---

```{r setup, include=FALSE}
library(tm)
library(qdap)
library(wordcloud)
library(plotrix)
```

Term frequency plots with tm
```{r}
#Covert TDM to matrix
coffee_m <- as.matrix(coffee_tdm)
#Sum rows and sort by frequency
term_frequency <-  rowSums(coffee_m)
term_frequency <- sort(term_frequency, decreasing = TRUE)

# Create a barplot
barplot(term_frequency[1:10], #indexing the number of terms, one to ten 
        col = "tan", # specify the color "tan"
        las = 2) # label orientation 2 to make the axis labels vertical

```

# Term frequency plots with qdap:
qdap provides the freq_terms function to get word frequency. 
```{r}
# Find term frequencies
frequency <-  freq_terms(
  tweets$text,
  top = 10, # specifies the top x number of words you want in your plot
  at.least =3, # tells the function a word should only appear if it occurs this number of times or more. 
  stopwords = "Top200Words" #uses a predefined list of words to remove called Top200Words.
)

#Plot term frequencies
plot(frequency)
```

```{r}
# Create frequency
frequency <- freq_terms(
    tweets$text,
    top = 10,
    at.least =3,
    stopwords("english") #This time use stopwords("english") to define stop words.
)

# Make a frequency bar chart
plot(frequency)
```

# Intro to word clouds
```{r}
#Convert TDM to matrix
chardonnay_tdm <-  TermDocumentMatrix(clean_chardonnay)
chardonnay_m <-  as.matrix(chardonnay_tdm)

#Sum rows and sort by frequency
term_frequency <-  rowSums(chardonnay_m)
word_freqs <-  data.frame(term = names(term_frequency),
                          num=term_frequency)

# Make word cloud
wordcloud(word_freqs$term, word_freqs$num, 
          max.words = 100, color = "red")
```

Another example
```{r}
# Print the first 10 entries in term_frequency
term_frequency[1:10]

# Vector of terms
terms_vec <- names(term_frequency)

# Create a word cloud for the values in word_freqs
wordcloud(terms_vec, term_frequency, 
          max.words = 50, color = "red")
```

# Stop wrods and word clouds
```{r}
# Review a "cleaned" tweet
content(chardonnay_corp[[24]])

# Add Chardonnay to stopwords
stops <- c(stopwords(kind = 'en'), "chardonnay")

# Review last 6 stopwords 
tail(stops)

# Apply to a corpus
cleaned_chardonnay_corp <- tm_map(chardonnay_corp, removeWords, stops)

# Review a "cleaned" tweet again
content(cleaned_chardonnay_corp[[24]])
```

# Plot the better word cloud
```{r}
# Sort the chardonnay_words in descending order
sorted_chardonnay_words <- sort(chardonnay_words, decreasing = TRUE)

# Print the 6 most frequent chardonnay terms
head(sorted_chardonnay_words)

# Get a terms vector
terms_vec <- names(chardonnay_words)

# Create a wordcloud for the values in word_freqs
wordcloud(terms_vec, chardonnay_words, 
          max.words = 50, colors = "red")
```

# multiple colors of word cloud

```{r}
# Print the word cloud with the specified colors
wordcloud(chardonnay_freqs$term, chardonnay_freqs$num,
   max.words = 100,
    colors = c("grey80", "darkgoldenrod1", "tomato"))

```

Another example
```{r}
# Select 5 colors 
color_pal <- cividis(n = 5)

# Examine the palette output
color_pal 

# Create a word cloud with the selected palette
wordcloud(chardonnay_freqs$term, 
chardonnay_freqs$num, 
max.words = 100, colors = color_pal)
```

# Other word clouds and word networks
```{r Commonality clouds}
#Combine both corpora: all_tweets
all_coffee <-  paste(coffee_tweets$text,
                     collapse = "")
all_chardonnay <- paste(chardonnay_tweets$text,
                        collapse = "")
#paste() together all the tweets in each corpus along with the parameter collapse = "". This collapses all tweets into a single vector. Then you can create a single vector containing the two collapsed documents.

#concatenate them
all_tweets <-  c(all_coffee, all_chardonnay)

#Clean all tweets
all_tweets <- VectorSource(all_tweets)
all_corpus <-  VCorpus(all_tweets)
all_clean <-  clean_corpus(all_corpurs)
all_tdm <-  TermDocumentMatrix(all_clean)
all_m <-  as.matrix(all_tdm)

#Make commonality cloud
commonality.cloud(all_m, colors = "Steelblue1", max.words = 100)
```

# Comparison Clouds
```{r Comparison Clouds}
#Combine both corpora: all_tweets
all_coffee <-  paste(coffee_tweets$text,
                     collapse = "")
all_chardonnay <- paste(chardonnay_tweets$text,
                        collapse = "")
#concatenate them
all_tweets <-  c(all_coffee, all_chardonnay)

#Clean all tweets
all_tweets <- VectorSource(all_tweets)
all_corpus <-  VCorpus(all_tweets)
all_clean <-  clean_corpus(all_corpurs)
all_tdm <-  TermDocumentMatrix(all_clean)
colnames(all_tdm) <-  c("coffee", "chardonnay") #specify the variables
all_m <-  as.matrix(all_tdm)

# Make comparison cloud
comparison.cloud(all_m, colors = c("orange", "blue"), 
                 max.words = 50)

#The comparison-cloud function will identify the words that are dissimilar, Term1 and Term_N, to make the plot.
```

# Pyramid plots:
Another way to visualize the conjunction of two corpora is with a polarized tag plot. 
```{r}
#Identify terms shared by both documents
common_words <-  subset(
  all_tdm_m,
  all_tdm_m[, 1] > 0 & all_tdm_m[, 2] >0
)

#Find the most commonly shared words
difference <-  abs(common_words[, 1] - common_words[, 2])
common_words <-  cbind(common_words, difference)
common_words <- common_words[order(common_words[, 3],
                                   decreasing =TRUE), ]
top25_df <-  data.frame(x = common_words[1:25, 1],
                        y = common_words[1:25, 2],
                        labels = rownames(common_words[1:25 ]))

#Make pyramid plot
pyramid.plot(top25_df$x, top25_df$y,
              labels = top25_df$labels,
              main = "Words in Common",
              gap =8, laxly = NULL,
              raxlab = NULL, unit = NULL,
              top.labels = c("Chardonnay",
                             "Words", 
                             "Coffee"))

```

# Word networkds
```{r}
# Create word network

word_associate(coffee_tweets$text,
               match.string = c("barista"),
               stopwrods = c(Top200Words, "coffee", "amp"),
               network.plot =  TRUE,
               cloud.colors =  c("gray85", "darkred"))

# Add a title
title(main =" Barista Coffee Tweet Associations")
```

